Fisher vector places: learning compact descriptors for place recognition

### 2014-11-14 cvpr15review.tex
small edits result section

      \paragraph{Bag-of-visual-words.}
         \textcolor{petr}{
            For bag of visual words image representation we provide three kind of results summarized in table \ref{tab:recallBOW}. First, similarly to \cite{Gronat13}, we compare the proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW). We observe improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM). Secondly, the results are also confronted to the p-value calibration of \cite{Gronat13}. The p-value calibration (BOW p-val) gives marginally better results (33.0\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images. Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) with no calibration. As reported in \cite{Gronat13}, we observe that using raw SVM scores directly with no calibration does not perform on BOW. However, this method gives satisfiable good results on Fisher vectors. Details are given next.
         }

         \begin{table}[b]
            \begin{centering}
               \include{table25kBOW}
            \caption{ \textbf{Results on Pittsburgh 25k dataset - BOW.}
                  The fraction of correctly recognized queries (recall@K)
                  \textcolor{petr}{
                     in the top $K\in\{1,2,5,10,20\}$ retrieved images.
                     % Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions. The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
                  } 
                  The learnt descriptors by the proposed method (BOW e-SVM) marginally improves over the raw bag-of-visual-words descriptors (BOW).
%                   on both the 25k and 55k Pittsburgh image datasets.     
            }
            \label{tab:recallBOW}
            \end{centering}
         \end{table}

@@

         Table \ref{tab:recall} summarizes the results of proposed method that has been applied on Fisher vectors for several target dimensions $d\in\{128,512,2048\}$. The learnt image representation (FV e-SVM) significantly outperforms the Fisher vector baseline (FV). The improvements are consistent across different lengths $K$ of the shortlist for all target dimensions of the Fisher vectors.
         Figure \ref{fig:recall} shows the results in a form of curve and it clearly demonstrates the benefits of the learnt descriptors. For comprehensiveness the figure also shows the BOW baseline curve taken from table \ref{tab:recallBOW} shown in black.

@@

         The p-val calibration of~\cite{Gronat13} has been also tested on e-SVM Fisher vectors. We found that the calibration did not perform well for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128). When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data.

@@

         Next, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration on Fisher vectors. We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM, talbe~\ref{tab:recallBOW}), as reported in \cite{Gronat13}, it marginally improves the recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).

@@

         Finally, we performed experiments on the larger Pittsburgh 55k dataset. Similarly to the former dataset, the results summarized in table \ref{tab:recall2} show consistent improvement of the proposed method (FV e-SVM) over the Fisher vector baseline (FV) across all target dimensions. The benefits of the proposed method in terms of memory efficiency will be discussed next.

@@

>>>>

      \paragraph{Bag-of-visual-words.}
         \textcolor{petr}{
            For the bag-of-visual-words image representation we provide three kinds of results summarized in table \ref{tab:recallBOW}. First, we compare the proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW). We observe an improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM). Secondly, the results are also compared to the p-value calibration from~\cite{Gronat13}. The p-value calibration (BOW p-val) gives marginally better results for small short lists (33.0\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images. Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) with no calibration. As reported in \cite{Gronat13}, we observe that using raw SVM scores directly with no calibration does not perform well for the bag-of-visual-words representation. %We describe results on Fisher vectors next. %However, this method gives satisfiable good results on Fisher vectors. Details are given next.
         }

         \begin{table}[b]
            \begin{centering}
               \include{table25kBOW}
            \caption{ \textbf{Results on Pittsburgh 25k dataset - BOW.}
                  The fraction of correctly recognized queries (recall@K)
                  \textcolor{petr}{
                     in the top $K\in\{1,2,5,10,20\}$ retrieved images.
                     % Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions. The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
                  } 
                  The learnt descriptors by the proposed method (BOW e-SVM) marginally improve over the raw bag-of-visual-words descriptors (BOW).
%                   on both the 25k and 55k Pittsburgh image datasets.     
            }
            \label{tab:recallBOW}
            \end{centering}
         \end{table}

@@

         Table \ref{tab:recall} summarizes results of the proposed method applied to Fisher vectors for several target dimensions $d\in\{128,512,2048\}$. The learnt image representation (FV e-SVM) significantly outperforms the Fisher vector baseline (FV). The improvements are consistent across different lengths $K$ of the shortlist for all target dimensions of the Fisher vectors.
         Figure \ref{fig:recall} shows the results in the form of a curve and it clearly demonstrates the benefits of the learnt descriptors. 
%         For completeness the figure also shows the BOW baseline curve taken from table \ref{tab:recallBOW} shown in black.

@@

         We have also tested on the learnt e-SVM Fisher vectors the p-val calibration of~\cite{Gronat13}. We found that the calibration did not perform well for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128). When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data.

@@

         Next, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration. We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM, talbe~\ref{tab:recallBOW}), as reported in \cite{Gronat13}, it marginally improves the recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).

@@

         Finally, we performed experiments on the larger Pittsburgh 55k dataset. The results are summarized in table \ref{tab:recall2} and show a consistent improvement of the proposed method (FV e-SVM) over the Fisher vector baseline (FV) across all target dimensions. 
%         The benefits of the proposed method in terms of memory efficiency will be discussed next.

@@

	% Additional results are given in supplementary material.
